Astr 513: Final Project

### 2016-05-06 Final_Project/ms.tex
Added filler tables to the tex file for fit results

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
figures \autoref{fig:cmatrix_betoule} and \autoref{fig:cmatrix_rest}.
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Betoule_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{betoule2014} sample. Overall very few correlations exist between
    samples, likely due to the averaging over redshift bins.}
  \label{fig:cmatrix_betoule}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Rest_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{rest2014} sample. Significant correlation exist between
    different samples due to dependencies on systematic variables
    as seen in \autoref{eq:RestCovMatrix}.}
  \label{fig:cmatrix_rest}
\end{figure}

@@

>>>>

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
figures \autoref{fig:cmatrix_betoule} and \autoref{fig:cmatrix_rest}.
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Betoule_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{betoule2014} sample. Overall very few correlations exist between
    samples, likely due to the averaging over redshift bins.}
  \label{fig:cmatrix_betoule}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Rest_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{rest2014} sample. Significant correlation exists between
    different samples due to dependencies on systematic variables
    as seen in \autoref{eq:RestCovMatrix}.}
  \label{fig:cmatrix_rest}
\end{figure}

@@

\EW{Filler table for the lambda CDM fits}
\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}$\Lambda$CDM best fit values}
\end{table}

\EW{Just a filler for the table for the wCDM fits}
\begin{table}[h]
   \centering
    \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \end{tabular}
    \caption {\label{tab:wcdm}wCDM best fit values}
\end{table}
